#__Setup__
## Set working directory, import libraries, read in data
```{r}
setwd("C:/Users/Ryan/Documents/GitHub/nitro/data")
library(readr)
library(ggplot2)
library(dplyr)
library(gridExtra)
library(ggfortify)
library(grid)
allrows<- read_tsv("C:/Users/Ryan/Documents/GitHub/nitro/data/allrows.tsv")
weather<-read_tsv("precipitation.tsv.txt")
weather$time<- as.POSIXct(strptime(weather$time, format = "%m/%d/%Y %H:%M"))
```

#__Show precipitation pattern__
## Isolate drydown period, add cumulative sum column
```{r}
weather<- weather %>% filter(time>= "2017-09-23 00:00:00" & time<= "2017-10-16 23:30:30") %>% mutate(cumulative = cumsum(precipitation))
```

## Graph cumulative precipitation
```{r}
png("Fig0.png", height = 6, width = 6, unit = "in", res=500)
ggplot(data = weather, aes(x = time, y = cumulative))+
  geom_area(fill = "lightblue")+
  labs(x = "", y = "Total Precipitation (mm)")+
  scale_y_continuous(breaks=seq(0,30,5))
dev.off()
```

## Total precipitation during drydown
```{r}
sum(weather$precipitation)
```

## Isolate drydown period
```{r}
dryDownData<- allrows %>% filter(time>= "2017-09-23 00:00:00" & time<= "2017-10-16 23:30:30")
```

## Check out column names
```{r}
names(dryDownData)
```

## Change columns from character to numeric
```{r}
dryDownData$vwc_64<- as.numeric(dryDownData$vwc_64)
dryDownData$vwc_150<- as.numeric(dryDownData$vwc_150)
dryDownData$vwc_300<- as.numeric(dryDownData$vwc_300)
dryDownData$pot_64<- as.numeric(dryDownData$pot_64)
dryDownData$pot_150<- as.numeric(dryDownData$pot_150)
dryDownData$pot_300<- as.numeric(dryDownData$pot_300)
dryDownData$ec_64<- as.numeric(dryDownData$ec_64)
dryDownData$ec_150<- as.numeric(dryDownData$ec_150)
dryDownData$ec_300<- as.numeric(dryDownData$ec_150)
dryDownData$ndvi<- as.numeric(dryDownData$ndvi)
dryDownData$temp_body<- as.numeric(dryDownData$temp_body)
```

#__Figure 1__
## Select measured plots
```{r}
plot43Low<- dryDownData %>% filter(location == "p43")

plot53High<- dryDownData %>% filter(location == "p53")

plot63Full<- dryDownData %>% filter(location == "p63")
```

## Create VWC graphs for each plot
```{r ggplot}
vwcLow<- ggplot(plot43Low, aes(x = time))+
  geom_line(aes(y = vwc_64, color = "64mm"))+
  geom_line(aes(y = vwc_150, color = "150mm"))+
  geom_line(aes(y = vwc_300, color = "300mm"))+scale_colour_manual("", values = c("64mm" = "yellow", "150mm" = "orange", "300mm" = "red")) +
  ylim(0.1, 0.45)+
  labs(x = "", y = "VWC", color = "Sensor Depth")+ theme(axis.text = element_text(size = 8), axis.title = element_text(size = 10), legend.position = "bottom")+ 
    scale_color_discrete(breaks=c("64mm","150mm","300mm"))

vwcHigh<- ggplot(plot53High, aes(time))+
  geom_line(aes(y = vwc_64, color = "64mm"))+
  geom_line(aes(y = vwc_150, color = "150mm"))+
  geom_line(aes(y = vwc_300, color = "300mm"))+
  scale_colour_manual("", values = c("64mm" = "yellow", "150mm" = "orange", "300mm" = "red"))+
  ylim(0.10, 0.45)+
  labs(x = "", y = "VWC", color = "Sensor Depth")+ theme(axis.text = element_text(size = 8), axis.title = element_text(size = 10))+
    scale_color_discrete(breaks=c("64mm","150mm","300mm"))

vwcFull<- ggplot(plot63Full, aes(time))+
  geom_line(aes(y = vwc_64, color = "64mm"))+
  geom_line(aes(y = vwc_150, color = "150mm"))+
  geom_line(aes(y = vwc_300, color = "300mm"))+
  ylim(0.10, 0.45)+
  labs(x = "", y = "VWC", color = "Sensor Depth")+
  scale_colour_manual("", values = c("64mm" = "yellow", "150mm" = "orange", "300mm" = "red")) + theme(axis.text = element_text(size = 8), axis.title = element_text(size = 10))+ 
    scale_color_discrete(breaks=c("64mm","150mm","300mm"))
```

## Create AWC graphs for each plot
```{r}
wpLow<- ggplot(plot43Low, aes(x = time))+
  geom_line(aes(y = pot_64, color = "64mm"))+
  geom_line(aes(y = pot_150, color = "150mm"))+
  geom_line(aes(y = pot_300, color = "300mm"))+scale_colour_manual("", values = c("64mm" = "yellow", "150mm" = "orange", "300mm" = "red")) +
  ylim(-200, 0)+
  labs(x = "", y = "AWC (kPa)", color = "Sensor Depth")+ theme(axis.text = element_text(size = 8), axis.title = element_text(size = 10))+ 
    scale_color_discrete(breaks=c("64mm","150mm","300mm"))

wpHigh<- ggplot(plot53High, aes(time))+
  geom_line(aes(y = pot_64, color = "64mm"))+
  geom_line(aes(y = pot_150, color = "150mm"))+
  geom_line(aes(y = pot_300, color = "300mm"))+
  scale_colour_manual("", values = c("64mm" = "yellow", "150mm" = "orange", "300mm" = "red"))+
  ylim(-200,0)+
  labs(x = "", y = "AWC (kPa)", color = "Sensor Depth")+ theme(axis.text = element_text(size = 8), axis.title = element_text(size = 10))+ 
    scale_color_discrete(breaks=c("64mm","150mm","300mm"))

wpFull<- ggplot(plot63Full, aes(time))+
  geom_line(aes(y = pot_64, color = "64mm"))+
  geom_line(aes(y = pot_150, color = "150mm"))+
  geom_line(aes(y = pot_300, color = "300mm"))+
  labs(x = "", y = "AWC (kPa)", color = "Sensor Depth")+
  ylim(-200, 0)+
  scale_colour_manual("", values = c("64mm" = "yellow", "150mm" = "orange", "300mm" = "red")) + theme(axis.text = element_text(size = 8), axis.title = element_text(size = 10))+ 
    scale_color_discrete(breaks=c("64mm","150mm","300mm"))
```

## Create EC graphs for each plot (currently unused)
```{r}
ecLow<- ggplot(plot43Low, aes(x = time))+
  geom_line(aes(y = ec_64, color = "64mm"))+
  geom_line(aes(y = ec_150, color = "150mm"))+
  geom_line(aes(y = ec_300, color = "300mm"))+scale_colour_manual("", values = c("64mm" = "yellow", "150mm" = "orange", "300mm" = "red")) +
  ylim(.02, .2)+
  labs(x = "", y = "kPa", color = "Sensor Depth")+ theme(legend.position = "bottom")

ecHigh<- ggplot(plot53High, aes(time))+ 
  geom_line(aes(y = ec_64, color = "64mm"))+
  geom_line(aes(y = ec_150, color = "150mm"))+
  geom_line(aes(y = ec_300, color = "300mm"))+
  scale_colour_manual("", values = c("64mm" = "yellow", "150mm" = "orange", "300mm" = "red"))+
  ylim(.02, .2)+
  labs(x = "", y = "kPa", color = "Sensor Depth")+ theme(legend.position = "bottom")

ecFull<- ggplot(plot63Full, aes(time))+
  geom_line(aes(y = ec_64, color = "64mm"))+
  geom_line(aes(y = ec_150, color = "150mm"))+
  geom_line(aes(y = ec_300, color = "300mm"))+
  labs(x = "", y = "kPa", color = "Sensor Depth")+
  ylim(.02, .2)+
  scale_colour_manual("", values = c("64mm" = "yellow", "150mm" = "orange", "300mm" = "red")) + theme(legend.position = "bottom")
```

## Create a shared legend
```{r}
g_legend<-function(a.gplot){
  tmp <- ggplot_gtable(ggplot_build(a.gplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)}

mylegend<-g_legend(vwcLow)
```

## Write out figure 1
```{r}
png("Fig1.png", height = 6, width = 6, unit = "in", res=500)
grid.arrange(arrangeGrob(arrangeGrob(vwcLow + theme(legend.position = "none"),wpLow+ theme(legend.position = "none"), ncol = 1, top = "Low Irrigation"),arrangeGrob(vwcFull + theme(legend.position = "none"), wpFull+ theme(legend.position = "none"), ncol =1, top = "Full Irrigation"), arrangeGrob(vwcHigh+theme(legend.position = "none"), wpHigh+ theme(legend.position = "none"), ncol = 1, top = "High Irrigation"), nrow = 1), mylegend, nrow = 2, heights = c(30, 1))
dev.off()
```

#__Figure 2__
## Seperate water treatments within excessive nitrogen, get average VWC, combine summary data
```{r}
lowWater<-  dryDownData %>% filter(irrigation_treatment == "low" & nitrogen_treament == "excessive") %>% group_by(time) %>% summarise(mean(vwc_64, na.rm = TRUE))
fullWater<- dryDownData %>% filter(irrigation_treatment == "full" & nitrogen_treament == "excessive") %>% group_by(time) %>% summarise(mean(vwc_64, na.rm = TRUE))
highWater<- dryDownData %>% filter(irrigation_treatment == "high" & nitrogen_treament == "excessive")%>% group_by(time) %>% summarise(mean(vwc_64, na.rm = TRUE))

highNitrogenMeans<- merge(x = lowWater, y = fullWater, by = "time")
highNitrogenMeans<- merge(x = highNitrogenMeans, y = highWater, by = "time")
names(highNitrogenMeans)<- c("time", "lowWater", "fullWater", "highWater")
```

## Graph VWC averages for excessive nitrogen
```{r}
highNVWC<- ggplot(highNitrogenMeans, aes(x = time))+
  geom_line(aes(y = lowWater, color = "low"))+
  geom_line(aes(y = fullWater, color = "full"))+
  geom_line(aes(y = highWater, color = "high"))+
  labs(x = "", y = "Average VWC", title = "Excessive Nitrogen", color = "Irrigation Treatment")+ theme(legend.position = "bottom", axis.text = element_text(size = 8), axis.title = element_text(size = 10))+ scale_color_discrete(breaks=c("low","full","high")) +
  ylim(0.1, 0.3)
```

## Seperate water treatments within optimum nitrogen, get average VWC, combine summary data
```{r}
lowWater<-  dryDownData %>% filter(irrigation_treatment == "low" & nitrogen_treament == "optimum") %>% group_by(time) %>% summarise(mean(vwc_64, na.rm = TRUE))
fullWater<- dryDownData %>% filter(irrigation_treatment == "full" & nitrogen_treament == "optimum") %>% group_by(time) %>% summarise(mean(vwc_64, na.rm = TRUE))
highWater<- dryDownData %>% filter(irrigation_treatment == "high" & nitrogen_treament == "optimum")%>% group_by(time) %>% summarise(mean(vwc_64, na.rm = TRUE))

optimumNitrogenMeans<- merge(x = lowWater, y = fullWater, by = "time")
optimumNitrogenMeans<- merge(x = optimumNitrogenMeans, y = highWater, by = "time")
names(optimumNitrogenMeans)<- c("time", "lowWater", "fullWater", "highWater")
```

## Graph VWC averages for optimum nitrogen
```{r}
optimumNVWC<- ggplot(optimumNitrogenMeans, aes(x = time))+
  geom_line(aes(y = lowWater, color = "low"))+
  geom_line(aes(y = fullWater, color = "full"))+
  geom_line(aes(y = highWater, color = "high"))+
  labs(x = "", y = "Average VWC", title = "Optimum Nitrogen", color = "Irrigation Treatment")+ theme(legend.position = "bottom", axis.text = element_text(size = 8), axis.title = element_text(size = 10))+ scale_color_discrete(breaks=c("low","full","high"))+
  ylim(0.1, 0.3)
```

## Seperate water treatments within deficient nitrogen, get average VWC, combine summary data
```{r}
lowWater<-  dryDownData %>% filter(irrigation_treatment == "low" & nitrogen_treament == "deficient") %>% group_by(time) %>% summarise(mean(vwc_64, na.rm = TRUE))
fullWater<- dryDownData %>% filter(irrigation_treatment == "full" & nitrogen_treament == "deficient") %>% group_by(time) %>% summarise(mean(vwc_64, na.rm = TRUE))
highWater<- dryDownData %>% filter(irrigation_treatment == "high" & nitrogen_treament == "deficient")%>% group_by(time) %>% summarise(mean(vwc_64, na.rm = TRUE))

deficientNitrogenMeans<- merge(x = lowWater, y = fullWater, by = "time")
deficientNitrogenMeans<- merge(x = deficientNitrogenMeans, y = highWater, by = "time")
names(deficientNitrogenMeans)<- c("time", "lowWater", "fullWater", "highWater")
```

## Graph VWC averages for deficient nitrogen
```{r}
deficientNVWC<- ggplot(deficientNitrogenMeans, aes(x = time))+
  geom_line(aes(y = lowWater, color = "low"))+
  geom_line(aes(y = fullWater, color = "full"))+
  geom_line(aes(y = highWater, color = "high"))+
  labs(x = "", y = "Average VWC", title = "Deficient Nitrogen", color = "Irrigation Treatment") + theme(legend.position = "bottom", axis.text = element_text(size = 8), axis.title = element_text(size = 10))+ scale_color_discrete(breaks=c("low","full","high"))+
  ylim(0.1, 0.3)
```

## Create combined legend
```{r}
mylegend2<-g_legend(deficientNVWC)
```

## Write out Figure 2A
```{r}
png("Fig2A.png", height = 6, width = 6, unit = "in", res=500)
grid.arrange(arrangeGrob(deficientNVWC+ theme(legend.position = "none"), optimumNVWC + theme(legend.position = "none"), highNVWC + theme(legend.position = "none")), mylegend2, ncol = 1, heights = c(30, 1))
dev.off()
```

## Seperate nitrogen treatments within high water, get average VWC, combine summary data
```{r}
deficient<-  dryDownData %>% filter(irrigation_treatment == "high" & nitrogen_treament == "deficient") %>% group_by(time) %>% summarise(mean(vwc_64, na.rm = TRUE))
optimum<- dryDownData %>% filter(irrigation_treatment == "high" & nitrogen_treament == "optimum") %>% group_by(time) %>% summarise(mean(vwc_64, na.rm = TRUE))
excessive<- dryDownData %>% filter(irrigation_treatment == "high" & nitrogen_treament == "excessive")%>% group_by(time) %>% summarise(mean(vwc_64, na.rm = TRUE))

highWaterMeans<- merge(x = deficient, y = optimum, by = "time")
highWaterMeans<- merge(x = highWaterMeans, y = excessive, by = "time")
names(highWaterMeans)<- c("time", "deficient", "optimum", "excessive")
```

## Graph VWC averages for excessive nitrogen
```{r}
highWVWC<- ggplot(highWaterMeans, aes(x = time))+
  geom_line(aes(y = deficient, color = "deficient"))+
  geom_line(aes(y = optimum, color = "optimum"))+
  geom_line(aes(y = excessive, color = "excessive"))+
  labs(x = "", y = "Average %VWC", title = "High Water", color = "Nitrogen Treatment")+ theme(legend.position = "bottom", axis.text = element_text(size = 8), axis.title = element_text(size = 10))+ scale_color_discrete(breaks=c("deficient","optimum","excessive")) +
  ylim(0.1, 0.3)
```

## Seperate water treatments within full water, get average VWC, combine summary data
```{r}
deficient<-  dryDownData %>% filter(irrigation_treatment == "full" & nitrogen_treament == "deficient") %>% group_by(time) %>% summarise(mean(vwc_64, na.rm = TRUE))
optimum<- dryDownData %>% filter(irrigation_treatment == "full" & nitrogen_treament == "optimum") %>% group_by(time) %>% summarise(mean(vwc_64, na.rm = TRUE))
excessive<- dryDownData %>% filter(irrigation_treatment == "full" & nitrogen_treament == "excessive")%>% group_by(time) %>% summarise(mean(vwc_64, na.rm = TRUE))

fullWaterMeans<- merge(x = deficient, y = optimum, by = "time")
fullWaterMeans<- merge(x = fullWaterMeans, y = excessive, by = "time")
names(fullWaterMeans)<- c("time", "deficient", "optimum", "excessive")
```

## Graph VWC averages for full water
```{r}
fullWVWC<- ggplot(fullWaterMeans, aes(x = time))+
  geom_line(aes(y = deficient, color = "deficient"))+
  geom_line(aes(y = optimum, color = "optimum"))+
  geom_line(aes(y = excessive, color = "excessive"))+
  labs(x = "", y = "Average %VWC", title = "Full Water", color = "Nitrogen Treatment")+ theme(legend.position = "bottom", axis.text = element_text(size = 8), axis.title = element_text(size = 10))+ scale_color_discrete(breaks=c("deficient","optimum","excessive")) +
  ylim(0.1, 0.3)
```

## Seperate water treatments within low water, get average VWC, combine summary data
```{r}
deficient<-  dryDownData %>% filter(irrigation_treatment == "low" & nitrogen_treament == "deficient") %>% group_by(time) %>% summarise(mean(vwc_64, na.rm = TRUE))
optimum<- dryDownData %>% filter(irrigation_treatment == "low" & nitrogen_treament == "optimum") %>% group_by(time) %>% summarise(mean(vwc_64, na.rm = TRUE))
excessive<- dryDownData %>% filter(irrigation_treatment == "low" & nitrogen_treament == "excessive")%>% group_by(time) %>% summarise(mean(vwc_64, na.rm = TRUE))

lowWaterMeans<- merge(x = deficient, y = optimum, by = "time")
lowWaterMeans<- merge(x = lowWaterMeans, y = excessive, by = "time")
names(lowWaterMeans)<- c("time", "deficient", "optimum", "excessive")
```

## Graph VWC averages for low water
```{r}
lowWVWC<- ggplot(lowWaterMeans, aes(x = time))+
  geom_line(aes(y = deficient, color = "deficient"))+
  geom_line(aes(y = optimum, color = "optimum"))+
  geom_line(aes(y = excessive, color = "excessive"))+
  labs(x = "", y = "Average %VWC", title = "Low Water", color = "Nitrogen Treatment")+ theme(legend.position = "bottom", axis.text = element_text(size = 8), axis.title = element_text(size = 10))+ scale_color_discrete(breaks=c("deficient","optimum","excessive")) +
  ylim(0.1, 0.3)
```

## Create combined legend
```{r}
mylegend3<-g_legend(lowWVWC)
```

## Write out Figure 2B
```{r}
png("Fig2B.png", height = 6, width = 6, unit = "in", res=500)
grid.arrange(arrangeGrob(lowWVWC+ theme(legend.position = "none"), fullWVWC + theme(legend.position = "none"), highWVWC + theme(legend.position = "none")), mylegend3, ncol = 1, heights = c(30, 1))
dev.off()
```
#__Figure 3__
## Create new frames for each measured plot
```{r}
p13<- dryDownData %>% filter(location == "p13")
p23<- dryDownData %>% filter(location == "p23")
p33<- dryDownData %>% filter(location == "p33")
p43<- dryDownData %>% filter(location == "p43")
p53<- dryDownData %>% filter(location == "p53")
p63<- dryDownData %>% filter(location == "p63")
p73<- dryDownData %>% filter(location == "p73")
p83<- dryDownData %>% filter(location == "p83")
p93<- dryDownData %>% filter(location == "p93")
```

## Visualize all NDVI data for drydown period
```{r}
ggplot()+
  geom_line(data= p13, aes(x = time, y = ndvi, color = irrigation_treatment, linetype= nitrogen_treament))+
  geom_line(data= p23, aes(x = time, y = ndvi, color = irrigation_treatment, linetype= nitrogen_treament))+
  geom_line(data= p33, aes(x = time, y = ndvi, color = irrigation_treatment, linetype= nitrogen_treament))+
  geom_line(data= p43, aes(x = time, y = ndvi, color = irrigation_treatment, linetype= nitrogen_treament))+
  geom_line(data= p53, aes(x = time, y = ndvi, color = irrigation_treatment, linetype= nitrogen_treament))+
  geom_line(data= p63, aes(x = time, y = ndvi, color = irrigation_treatment, linetype= nitrogen_treament))+
  geom_line(data= p73, aes(x = time, y = ndvi, color = irrigation_treatment, linetype= nitrogen_treament))+
  geom_line(data= p83, aes(x = time, y = ndvi, color = irrigation_treatment, linetype= nitrogen_treament))+
  geom_line(data= p93, aes(x = time, y = ndvi, color = irrigation_treatment, linetype= nitrogen_treament))
```
## Isolate data from the last week of the drydown, only noon measurements
```{r}
periodOfInterest<- dryDownData %>% filter(time>= "2017-10-09 00:00:00" & time<= "2017-10-16 23:30:00")

noon<- periodOfInterest %>% filter(grepl("12:00:00",time)) %>% filter(!is.na(ndvi)) 
noon$nitrogen_treament <- factor(noon$nitrogen_treament, levels = c("deficient", "optimum", "excessive"))
```

## Read out Figure 3
```{r}
png("Fig3.png", height = 6, width = 6, unit = "in", res=500)
ggplot(noon, aes(x = nitrogen_treament, y = ndvi, group = location, fill = irrigation_treatment, color = nitrogen_treament))+
  geom_boxplot()+
  scale_fill_manual(name = "Irrigation Treatment", values = c("grey", "black", "white"), breaks = c("low", "full", "high"))+ 
  scale_color_manual(name = "", values = c("salmon", "forestgreen", "blue"), breaks = c("", "", ""))+ 
  labs(x = "Nitrogen Treatment", y = "NDVI")
dev.off()
```

#__Figure 4__
##Visualize canopy temperature data
```{r}
ggplot()+
  geom_line(data = p13, aes(x = time, y = temp_body, color = irrigation_treatment, linetype = nitrogen_treament))+
  geom_line(data = p23, aes(x = time, y = temp_body, color = irrigation_treatment, linetype = nitrogen_treament))+
  geom_line(data = p33, aes(x = time, y = temp_body, color = irrigation_treatment, linetype = nitrogen_treament))+
  geom_line(data = p43, aes(x = time, y = temp_body, color = irrigation_treatment, linetype = nitrogen_treament))+
  geom_line(data = p53, aes(x = time, y = temp_body, color = irrigation_treatment, linetype = nitrogen_treament))+
  geom_line(data = p63, aes(x = time, y = temp_body, color = irrigation_treatment, linetype = nitrogen_treament))+
  geom_line(data = p73, aes(x = time, y = temp_body, color = irrigation_treatment, linetype = nitrogen_treament))+
  geom_line(data = p83, aes(x = time, y = temp_body, color = irrigation_treatment, linetype = nitrogen_treament))+
  geom_line(data = p93, aes(x = time, y = temp_body, color = irrigation_treatment, linetype = nitrogen_treament))
```

## Use noon measurement for last week of drydown, create a table of averages over that time period for each treatment to identify a standard
```{r}
noon<- periodOfInterest %>% filter(grepl("12:00:00",time)) %>% filter(!is.na(temp_body))

averages<- noon %>% group_by(irrigation_treatment, nitrogen_treament) %>% summarise(mean(temp_body))
averages
```

## Create a new column with selected "standard" treatment (high irrigation and optimum nitrogen), create a new column ("normalized") with all temperature values subtracted from the standard, create factor levels for nitrogen treatment
```{r}
highAndOptimum <- noon %>% filter(irrigation_treatment == "high" & nitrogen_treament == "optimum") %>% select(time, temp_body)
names(highAndOptimum)<- c("time", "standard")
withStandard<- merge(noon, highAndOptimum, by = "time")
withStandard<- withStandard %>% select(time, nitrogen_treament, irrigation_treatment, standard, temp_body, location) %>% mutate(normalized = temp_body - standard)
withStandard$nitrogen_treament<- factor(withStandard$nitrogen_treament, levels = c("deficient", "optimum", "excessive"))
```

## Read out Figure 4
```{r}
png("Fig4.png", height = 6, width = 6, unit = "in", res=500)
ggplot(withStandard)+
  geom_boxplot(aes(x = nitrogen_treament, y = normalized, fill = irrigation_treatment, color = nitrogen_treament, group = location))+ 
  scale_fill_manual(name = "Irrigation Treatment", values = c("grey", "black", "white"), breaks = c("low", "full", "high"))+ 
  scale_color_manual(name = "", values = c("salmon", "forestgreen", "blue"), breaks = "")+ 
  labs(x = "Nitrogen Treatment", y = "Degrees above a non-stressed reference (Celsius)")+
  scale_y_continuous(breaks=seq(-0.5,3,.5))
dev.off()
```

#__ANOVA__
# ANOVA for NDVI and nitrogen treatment
```{r}
anovaFit<- aov(ndvi ~ nitrogen_treament, data = periodOfInterest)
summary(anovaFit)
```
# ANOVA for NDVI and irrigation treatment
```{r}
anovaFit2<- aov(ndvi ~ irrigation_treatment, data = periodOfInterest)
summary(anovaFit2)
```

# ANOVA for canopy temp and nitrogen treatment
```{r}
anovaFit3<- aov(normalized ~ nitrogen_treament, data = withStandard)
summary(anovaFit3)
```
# ANOVA for canopy temp and irrigation treatment
```{r}
anovaFit4<- aov(normalized ~ irrigation_treatment, data = withStandard)
summary(anovaFit4)
```