---
title: "NITRO"
author: "Hayley Mangleson & Justin Shattuck"
date: "3/28/2018"
output: html_document
# runtime: shiny
---

Run some python to clean up the filenames
```{python python.reticulate=FALSE}
import os
from os.path import isfile, join
import re
current = os.getcwd()
# print(current)
os.chdir('./data/test/') ###modify for prod
p = re.compile('.*\.csv$', re.IGNORECASE)
files = [f for f in os.listdir('.') if (isfile(join('.', f)) and p.match(f))]
# print(files)
p = re.compile('(^row\d[a-z]{0,4})', re.IGNORECASE)
counter = 0
for f in files:
  m = p.match(f)
  if m != None:
    os.rename(f, m.group().lower()[0:5] + '.csv')
    counter += 1
print('renamed ' + str(counter) + ' files')
```


Load necessary libraries for data tidying (install any that are missing).
```{r echo=FALSE}
if(!"readr" %in% rownames(installed.packages())) {
  install.packages("readr", repos="http://cran.us.r-project.org")
  print("installed readr")
} else {
  print("readr is already installed")
}
if(!"tidyr" %in% rownames(installed.packages())) {
  install.packages("tidyr", repos="http://cran.us.r-project.org")
  print("installed tidyr")
} else {
  print("tidyr is already installed")
}
if(!"ggplot2" %in% rownames(installed.packages())) {
  install.packages("ggplot2", repos="http://cran.us.r-project.org")
  print("installed ggplot")
} else {
  print("ggplot2 is already installed")
}
# if(!"rJava" %in% rownames(installed.packages())) {
#   install.packages("rJava", repos="http://cran.us.r-project.org", type="source")
#   print("installed rJava")
# } else {
#   print("rJava is already installed")
# }
# if(!"XLConnect" %in% rownames(installed.packages())) {
#   install.packages("XLConnect", repos="http://cran.us.r-project.org")
#   print("installed XLConnect")
# } else {
#   print("XLConnect is already installed")
# }

# dplyr
# stringr

# dyn.load('/Library/Java/JavaVirtualMachines/jdk1.8.0_25.jdk/Contents/Home/jre/lib/server/libjvm.dylib')
# require(rJava)


  
print("loading libraries")
library("readr")
library("tidyr")
library("rJava")
# library("XLConnect")
```


Choose a variable to plot:
```{r echo=FALSE, warning=FALSE, message=FALSE}
setwd("./data/test/")
row1f <- read_csv(file = "row1f.csv", col_names = FALSE, skip = 3, col_types = c(col_double(),col_double(),col_double(),col_double(),col_double(),col_double(),col_double(),col_double(),col_double(),col_double(),col_double(),col_double(),col_double(),col_double(),col_double()), na = "")

names(row1f) <- c("new_name", "another_new_name")
sapply(row1f, typeof)
# selectInput("data", "", c("co2", "lh"))

```

```{r}



```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

